\texttt{MSnbase}, efficient R-based processing and visualisation of raw mass spectrometry data

### 2020-04-27 msnbase2.Rnw
minor fixes

There exists a very diverse catalogue of software tools to explore,
process and interpret mass spectrometry data. These range from low
level software libraries that are aimed at programmers to develop new
applications, to user-oriented applications. Example of software
libraries include Java-based jmzML~\cite{Cote:2010} or C/C++-based
ProteoWizard~\cite{Chambers:2012}, that are used as application
programming interfaces. ProteomeDiscoverer (Thermo Scientific),
MaxQuant~\cite{Cox:2008} and PeptideShaker~\cite{Vaudel:2015} are
among the most widely user-centric application. They generally provide
a limited and fixed set of functionality featuring often advanced
graphical user interfaces (GUI).

In this software note, we present version 2 of the \texttt{MSnbase}
\cite{Gatto:2012} software package, available from the
Bioconductor~\cite{Huber:2015} project since 2011. \texttt{MSnbase},
like other Python-based software packages such as
{pyOpenMS}~\cite{Rost:2014}, spectrum\_utils~\cite{Bittremieux:2020}
or Pyteomics~\cite{Goloborodko:2013}, offers a platform that lies
between low level libraries and end-use software. \texttt{MSnbase}
provides a flexible R~\cite{R} command line environment for
metabolomics and proteomics mass spectrometry-based application. It
allows a detailed step-by-step processing, analysis and exploration of
the data and development of novel computational mass spectrometry
methods.

>>>>

There exists a very diverse catalogue of software tools to explore,
process and interpret mass spectrometry data. These range from low
level software libraries that are aimed at programmers to develop new
applications, to user-oriented applications. Example of software
libraries include Java-based jmzML~\cite{Cote:2010} or C/C++-based
ProteoWizard~\cite{Chambers:2012}, that are used as application
programming interfaces. ProteomeDiscoverer (Thermo Scientific),
MaxQuant~\cite{Cox:2008} and PeptideShaker~\cite{Vaudel:2015} are
among the most widely user-centric application. They generally provide
a limited and fixed set of functionality featuring often advanced
graphical user interfaces.

In this software note, we present version 2 of the \texttt{MSnbase}
\cite{Gatto:2012} software package, available from the
Bioconductor~\cite{Huber:2015} project. \texttt{MSnbase}, like other
Python-based software packages such as {pyOpenMS}~\cite{Rost:2014},
spectrum\_utils~\cite{Bittremieux:2020} or
Pyteomics~\cite{Goloborodko:2013}, offers a platform that lies between
low level libraries and end-use software. \texttt{MSnbase} provides a
flexible R~\cite{R} command line environment for metabolomics and
proteomics mass spectrometry-based application. It allows a detailed
step-by-step processing, analysis and exploration of the data and
development of novel computational mass spectrometry methods.
